### 2020-12-13 README.Rmd
new features

- `create_stateyears()`: converts Correlates of War or Gleditsch-Ward state membership data into state-year format.
- `create_dyadyears()`: converts Correlates of War or Gleditsch-Ward state system membership data into dyad-year format.

@@

- `cow_states`: Correlates of War state system membership data (version: 2016)
- `gw_states`: Gleditsch-Ward independent state system data (version: 2017)

>>>>

- `add_capital_distance()`: adds capital-to-capital distance (in kilometers, "as the crow flies") to dyad-year data.
- `create_stateyears()`: converts Correlates of War or Gleditsch-Ward state membership data into state-year format.
- `create_dyadyears()`: converts Correlates of War or Gleditsch-Ward state system membership data into dyad-year format.

@@

- `capitals`: a list of capitals and capital transition for Correlates of War state system members
- `cow_ddy`: a full directed dyad-year data frame of Correlates of War state system members
- `cow_states`: Correlates of War state system membership data (version: 2016)
- `gw_states`: Gleditsch-Ward independent state system data (version: 2017)
